Software Citation Principles

### 2016-07-25 sc-principles/software-citation-principles.tex
editing wording for explanation of historical use case

Researcher is engaged in historical/cultural research -- e.g., study of video games as cultural artifacts.

@@

Due to overlaps with use case 6, reproducing analysis, we decided not to include
this use case in the table.

>>>>

Researcher is engaged in historical/cultural research---e.g., study of video games as cultural artifacts.

@@

This overlaps with use case 6 (reproducing analysis), and so we decided not to
include this as a distinct use case.
